---
title: "Denver STAR Program: Neighborhood-Level Difference-in-Differences"
subtitle: "MGT 159T — Final Project"
date: today
format:
  pdf:
    toc: true
    number-sections: true
    fig-pos: "H"
    geometry: margin=1in
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(lubridate)
library(scales)
library(broom)
```

# Section 1: Describe the Raw Data

```{r}
#| label: load-data
#| include: false

# ----- DROPBOX LINK -----------------------------------------------------------
# Upload crime.csv to Dropbox, copy the share link, change ?dl=0 to ?dl=1,
# and paste it below.
dropbox_url <- "https://www.dropbox.com/scl/fi/mv53cxbuh157tumpx39s2/crime.csv?rlkey=q86k70ole8xkv6j9fe35walkt&st=uhlsatnl&dl=1"
# ------------------------------------------------------------------------------

crime_raw <- read_csv(
  dropbox_url,
  locale = locale(encoding = "latin1"),
  show_col_types = FALSE
)

crime <- crime_raw |>
  mutate(
    first_occurrence_date = mdy_hms(first_occurrence_date),
    reported_date         = mdy_hms(reported_date),
    last_occurrence_date  = mdy_hms(last_occurrence_date),
    year                  = year(first_occurrence_date)
  )

star_date <- as.Date("2020-06-01")

star_types <- c(
  "criminal-trespassing",
  "disturbing-the-peace",
  "criminal-mischief-other",
  "drug-poss-paraphernalia",
  "drug-methampetamine-possess",
  "drug-pcs-other-drug",
  "liquor-possession",
  "drug-heroin-possess",
  "drug-cocaine-possess",
  "drug-opium-or-deriv-possess",
  "drug-marijuana-possess",
  "drug-synth-narcotic-possess",
  "drug-hallucinogen-possess"
)

treated_nbhds <- c(
  "cbd", "union-station", "five-points", "civic-center",
  "capitol-hill", "north-capitol-hill", "cheesman-park", "city-park-west"
)
```

## Dataset Overview

The raw dataset contains **`r nrow(crime)`** incident records across
**`r ncol(crime)`** variables, spanning
**`r format(min(crime$first_occurrence_date, na.rm = TRUE), "%B %d, %Y")`**
to
**`r format(max(crime$first_occurrence_date, na.rm = TRUE), "%B %d, %Y")`**.
Each row is a single reported incident. The key fields used in this analysis
are `offense_type_id`, `neighborhood_id`, and `first_occurrence_date`.

## STAR-Targeted Offense Types

The 13 offense types below represent the non-violent substance use,
trespassing, and public disorder calls that match STAR's documented
eligibility criteria. These form the dependent variable.

```{r}
#| label: tbl-star-types
#| tbl-cap: "STAR-targeted offense types — count and share of all incidents"
crime |>
  filter(offense_type_id %in% star_types) |>
  count(offense_type_id, sort = TRUE) |>
  mutate(pct = round(100 * n / sum(n), 1)) |>
  rename(`Offense type` = offense_type_id, Count = n, `Share (%)` = pct) |>
  knitr::kable()
```

Total STAR-targeted incidents across all years:
**`r sum(crime$offense_type_id %in% star_types)`**.

## Top Neighborhoods by STAR-Targeted Offense Count

```{r}
#| label: tbl-top-nbhds
#| tbl-cap: "Top 10 neighborhoods by STAR-targeted offense count (2018–2021)"
crime |>
  filter(offense_type_id %in% star_types, year %in% 2018:2021) |>
  count(neighborhood_id, sort = TRUE) |>
  head(10) |>
  rename(Neighborhood = neighborhood_id, Count = n) |>
  knitr::kable()
```

## Treated Neighborhoods in the Data

The eight pilot neighborhoods are confirmed present in the dataset with the
following record counts:

```{r}
#| label: tbl-treated-check
#| tbl-cap: "Treated neighborhoods: raw incident counts"
crime |>
  filter(neighborhood_id %in% treated_nbhds) |>
  count(neighborhood_id) |>
  arrange(neighborhood_id) |>
  rename(Neighborhood = neighborhood_id, `Total incidents` = n) |>
  knitr::kable()
```

## Missing-Value Audit

```{r}
#| label: tbl-missing
#| tbl-cap: "Missing values by variable"
crime |>
  summarise(across(everything(), ~ sum(is.na(.)))) |>
  pivot_longer(everything(), names_to = "Variable", values_to = "N missing") |>
  mutate(`% missing` = round(100 * `N missing` / nrow(crime), 2)) |>
  arrange(desc(`N missing`)) |>
  knitr::kable()
```

## Figure B: STAR-Targeted Offenses Over Time (Raw Data)

```{r}
#| label: fig-figB
#| fig-cap: "Monthly STAR-targeted offenses — treated vs. control neighborhoods (raw data). Both lines are per-neighborhood averages."
#| fig-height: 4.5
crime |>
  filter(offense_type_id %in% star_types,
         first_occurrence_date >= as.POSIXct("2018-01-02"),
         first_occurrence_date <  as.POSIXct("2021-09-01"),
         !is.na(neighborhood_id)) |>
  mutate(
    year_month = floor_date(first_occurrence_date, "month"),
    group      = if_else(neighborhood_id %in% treated_nbhds,
                         "Treated (avg per pilot nbhd)",
                         "Control (avg per other nbhd)")
  ) |>
  count(group, neighborhood_id, year_month) |>
  group_by(group, year_month) |>
  summarise(mean_n = mean(n), .groups = "drop") |>
  ggplot(aes(x = as.Date(year_month), y = mean_n, colour = group)) +
  geom_line(linewidth = 1) +
  geom_vline(xintercept = star_date, linetype = "dashed", colour = "black") +
  annotate("text", x = star_date, y = Inf,
           label = "STAR launch\nJun 2020", hjust = -0.05, vjust = 1.3, size = 3) +
  scale_colour_manual(values = c("Treated (avg per pilot nbhd)" = "#2166ac",
                                 "Control (avg per other nbhd)" = "#d73027")) +
  scale_x_date(date_breaks = "6 months", date_labels = "%b %Y") +
  scale_y_continuous(labels = comma) +
  labs(x = NULL, y = "Avg monthly STAR-targeted incidents per neighborhood",
       colour = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))
```

\newpage

# Section 2: Sample Construction

## Filter Log

```{r}
#| label: filter-log
crime_step1 <- crime |>
  filter(first_occurrence_date >= as.POSIXct("2018-01-02"),
         first_occurrence_date <  as.POSIXct("2021-09-01"))

crime_step2 <- crime_step1 |>
  filter(!is.na(neighborhood_id))

tibble(
  Step = c("Raw data",
           "Step 1: Keep Jan 2, 2018 – Aug 31, 2021",
           "Step 2: Drop missing neighborhood_id"),
  `Rows remaining` = c(nrow(crime), nrow(crime_step1), nrow(crime_step2)),
  `Rows removed`   = c(0,
                       nrow(crime) - nrow(crime_step1),
                       nrow(crime_step1) - nrow(crime_step2)),
  `% removed`      = round(c(0,
                              100 * (nrow(crime) - nrow(crime_step1)) / nrow(crime),
                              100 * (nrow(crime_step1) - nrow(crime_step2)) / nrow(crime_step1)), 1)
) |>
  knitr::kable()
```

## Panel Construction

Step 1 retains the pilot window (January 2018 – August 2021) and excludes
the fall 2021 citywide expansion so that control neighborhoods remain
untreated for the full study period. Step 2 drops the
`r nrow(crime_step1) - nrow(crime_step2)` rows with a missing
`neighborhood_id` since treatment assignment is impossible without it.
Step 3 aggregates individual incidents to a neighborhood × month panel,
filling in zero-incident months explicitly so the regression sees them
rather than treating them as missing.

```{r}
#| label: build-panel
#| include: false
crime_clean <- crime_step2 |>
  mutate(
    year_month    = floor_date(first_occurrence_date, "month") |> as.Date(),
    treated       = as.integer(neighborhood_id %in% treated_nbhds),
    post_star     = as.integer(year_month >= star_date),
    did_term      = treated * post_star,
    star_targeted = as.integer(offense_type_id %in% star_types)
  )

analysis_panel <- crime_clean |>
  filter(star_targeted == 1) |>
  count(neighborhood_id, treated, year_month, name = "incidents") |>
  complete(
    neighborhood_id,
    year_month = seq(min(year_month), max(year_month), by = "month"),
    fill = list(incidents = 0)
  ) |>
  mutate(treated   = as.integer(neighborhood_id %in% treated_nbhds),
         post_star = as.integer(year_month >= star_date),
         did_term  = treated * post_star)
```

The final panel has **`r nrow(analysis_panel)`** cells
(**`r n_distinct(analysis_panel$neighborhood_id)`** neighborhoods ×
**`r n_distinct(analysis_panel$year_month)`** months), covering
**`r n_distinct(analysis_panel$neighborhood_id[analysis_panel$treated==1])`**
treated and
**`r n_distinct(analysis_panel$neighborhood_id[analysis_panel$treated==0])`**
control neighborhoods.

## Panel Summary Statistics

```{r}
#| label: tbl-panel-summary
#| tbl-cap: "Panel summary statistics by treatment group"
analysis_panel |>
  group_by(treated) |>
  summarise(
    `Neighborhoods`      = n_distinct(neighborhood_id),
    `Panel cells`        = n(),
    `Mean incidents`     = round(mean(incidents), 2),
    `SD incidents`       = round(sd(incidents), 2),
    `Min`                = min(incidents),
    `Max`                = max(incidents),
    `% zero-incident months` = round(100 * mean(incidents == 0), 1),
    .groups = "drop"
  ) |>
  mutate(treated = if_else(treated == 1, "Treated", "Control")) |>
  rename(Group = treated) |>
  knitr::kable()
```

## Baseline Comparability

DID requires parallel *trends*, not equal baseline *levels*. The table below
documents the pre-STAR level difference so readers can assess whether trend
parallelism is plausible. This difference motivates Robustness Check 4
(alternative control group restricted to high-volume neighborhoods).

```{r}
#| label: tbl-baseline
#| tbl-cap: "Baseline comparability — pre-STAR period (Jan 2018 – May 2020)"
analysis_panel |>
  filter(post_star == 0) |>
  group_by(treated) |>
  summarise(
    `Neighborhoods`  = n_distinct(neighborhood_id),
    `Mean incidents` = round(mean(incidents), 2),
    `Median`         = round(median(incidents), 2),
    `SD`             = round(sd(incidents), 2),
    .groups = "drop"
  ) |>
  mutate(Group = if_else(treated == 1, "Treated (8 pilot nbhds)",
                                       "Control (other nbhds)")) |>
  select(Group, everything(), -treated) |>
  knitr::kable()
```

\newpage

# Section 3: Analysis

## Identification Strategy

This analysis uses **difference-in-differences (DID)**. The key assumption
is **parallel trends**: absent STAR, STAR-targeted incidents in the 8 pilot
neighborhoods would have followed the same monthly trend as the control
neighborhoods. Neighborhood fixed effects absorb permanent cross-neighborhood
level differences (downtown neighborhoods always have higher crime volumes).
Month fixed effects absorb city-wide shocks common to all neighborhoods
(COVID-19, seasonality). The interaction term `treated × post-STAR` isolates
the pilot neighborhoods' deviation from the common trend after June 2020 —
the causal estimate of STAR's effect.

## Figure 1: Main Parallel-Trends Plot

```{r}
#| label: fig-1
#| fig-cap: "Monthly STAR-targeted offenses — 8 treated neighborhoods vs. control average. Both lines are per-neighborhood averages so the comparison is on equal footing."
#| fig-height: 4.5
analysis_panel |>
  group_by(treated, year_month) |>
  summarise(mean_inc = mean(incidents), .groups = "drop") |>
  mutate(Group = if_else(treated == 1,
                         "Treated (avg per pilot nbhd)",
                         "Control (avg per other nbhd)")) |>
  ggplot(aes(x = as.Date(year_month), y = mean_inc, colour = Group)) +
  geom_line(linewidth = 1.1) +
  geom_vline(xintercept = star_date, linetype = "dashed", colour = "black") +
  annotate("text", x = star_date, y = Inf,
           label = "STAR launch\nJun 2020", hjust = -0.05, vjust = 1.3, size = 3) +
  scale_colour_manual(values = c("Treated (avg per pilot nbhd)" = "#2166ac",
                                 "Control (avg per other nbhd)" = "#d73027")) +
  scale_x_date(date_breaks = "6 months", date_labels = "%b %Y") +
  scale_y_continuous(labels = comma) +
  labs(x = NULL, y = "Avg monthly STAR-targeted incidents per neighborhood",
       colour = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))
```

## Figure 2: Per-Neighborhood Facets

```{r}
#| label: fig-2
#| fig-cap: "STAR-targeted offenses per treated neighborhood, 2018–2021. Free y-axis per panel. Checks whether the post-STAR drop appears across all 8 neighborhoods or is driven by a subset."
#| fig-height: 5
analysis_panel |>
  filter(treated == 1) |>
  ggplot(aes(x = as.Date(year_month), y = incidents)) +
  geom_line(linewidth = 0.7, colour = "#2166ac") +
  geom_vline(xintercept = star_date, linetype = "dashed", colour = "black") +
  facet_wrap(~ neighborhood_id, scales = "free_y", ncol = 4) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  scale_y_continuous(labels = comma) +
  labs(x = NULL, y = "Monthly incidents") +
  theme_minimal(base_size = 9) +
  theme(axis.text.x  = element_text(angle = 45, hjust = 1),
        strip.text   = element_text(size = 8, face = "bold"))
```

## Main DID Regression

```{r}
#| label: did-regression
#| include: false
did_mod    <- lm(incidents ~ factor(neighborhood_id) + factor(year_month) + did_term,
                 data = analysis_panel)
did_result <- tidy(did_mod, conf.int = TRUE) |> filter(term == "did_term")
```

```{r}
#| label: tbl-did-results
#| tbl-cap: "Main DID regression results"
did_result |>
  select(Estimate = estimate, `Std. Error` = std.error,
         `t-stat` = statistic, `p-value` = p.value,
         `95% CI lower` = conf.low, `95% CI upper` = conf.high) |>
  mutate(across(everything(), \(x) round(x, 3))) |>
  knitr::kable()
```

The model has **`r nobs(did_mod)`** observations and an R² of
**`r round(summary(did_mod)$r.squared, 3)`**.

## Figure 3: DID Coefficient Plot

```{r}
#| label: fig-3
#| fig-cap: "DID estimate with 95% confidence interval. A negative estimate means treated neighborhoods saw a larger decline in STAR-targeted incidents than the control trend would predict."
#| fig-height: 3.5
#| fig-width: 4
ggplot(did_result,
       aes(x = "DID estimate", y = estimate, ymin = conf.low, ymax = conf.high)) +
  geom_pointrange(size = 1, colour = "#2166ac") +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey40") +
  scale_y_continuous(labels = comma) +
  labs(x = NULL,
       y = "Differential monthly STAR-targeted incidents\n(treated vs. control)") +
  theme_minimal(base_size = 11)
```

## Figure 4: Event-Study Plot

```{r}
#| label: fig-4
#| fig-cap: "Event-study plot. Each point is the treated-minus-control average gap for that month, normalised so May 2020 (month −1) = 0. A flat pre-period line supports parallel trends. Band = ±2 SD of pre-treatment variation."
#| fig-height: 4.5
event_gaps <- analysis_panel |>
  group_by(treated, year_month) |>
  summarise(mean_inc = mean(incidents), .groups = "drop") |>
  pivot_wider(names_from = treated, values_from = mean_inc, names_prefix = "g") |>
  rename(treated_avg = g1, control_avg = g0) |>
  mutate(
    months_to_star = 12L * (year(year_month) - 2020L) + (month(year_month) - 6L),
    gap            = treated_avg - control_avg
  )

ref_gap    <- event_gaps$gap[event_gaps$months_to_star == -1]
event_gaps <- event_gaps |> mutate(norm_gap = gap - ref_gap)
pre_sd     <- sd(event_gaps$norm_gap[event_gaps$months_to_star < 0])

ggplot(event_gaps, aes(x = months_to_star, y = norm_gap)) +
  annotate("rect", xmin = min(event_gaps$months_to_star), xmax = 0,
           ymin = -Inf, ymax = Inf, fill = "grey90", alpha = 0.5) +
  geom_ribbon(aes(ymin = norm_gap - 2 * pre_sd, ymax = norm_gap + 2 * pre_sd),
              alpha = 0.15, fill = "#2166ac") +
  geom_line(colour = "#2166ac", linewidth = 0.9) +
  geom_point(colour = "#2166ac", size = 1.8) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey40") +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "black") +
  annotate("text", x = 0,   y = Inf, label = "STAR launch",
           hjust = -0.05, vjust = 1.3, size = 3) +
  annotate("text", x = -14, y = Inf, label = "Pre-treatment\n(shaded)",
           hjust = 0.5, vjust = 1.3, size = 3, colour = "grey40") +
  scale_y_continuous(labels = comma) +
  labs(x = "Months relative to STAR launch  (0 = June 2020)",
       y = "Normalised gap (treated avg − control avg)") +
  theme_minimal(base_size = 11)
```

## Robustness Checks

### Check 1: Pre-Treatment Parallel Trends

```{r}
#| label: fig-rob1
#| fig-cap: "Pre-treatment parallel trends (Jan 2018 – May 2020). Lines should move in parallel; a common slope supports the DID parallel-trends assumption."
#| fig-height: 3.5
analysis_panel |>
  filter(year_month < star_date) |>
  group_by(treated, year_month) |>
  summarise(mean_inc = mean(incidents), .groups = "drop") |>
  mutate(Group = if_else(treated == 1, "Treated (avg)", "Control (avg)")) |>
  ggplot(aes(x = as.Date(year_month), y = mean_inc, colour = Group, group = Group)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5) +
  scale_colour_manual(values = c("Treated (avg)" = "#2166ac",
                                 "Control (avg)" = "#d73027")) +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y") +
  scale_y_continuous(labels = comma) +
  labs(x = NULL, y = "Avg monthly STAR-targeted incidents per nbhd", colour = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))
```

### Check 2: Placebo Test (Fake Treatment = June 2019)

If the pre-period trends are truly parallel, running the same DID with a
fake treatment date one year before the actual launch should produce an
insignificant estimate.

```{r}
#| label: placebo
#| include: false
placebo_panel <- crime_clean |>
  filter(star_targeted == 1, year_month < star_date) |>
  mutate(post_placebo = as.integer(year_month >= as.Date("2019-06-01")),
         did_placebo  = treated * post_placebo) |>
  count(neighborhood_id, treated, post_placebo, did_placebo, year_month,
        name = "incidents") |>
  complete(neighborhood_id,
           year_month = seq(min(year_month), max(year_month), by = "month"),
           fill = list(incidents = 0)) |>
  mutate(treated      = as.integer(neighborhood_id %in% treated_nbhds),
         post_placebo = as.integer(year_month >= as.Date("2019-06-01")),
         did_placebo  = treated * post_placebo)

did_mod_placebo <- lm(incidents ~ factor(neighborhood_id) + factor(year_month) + did_placebo,
                      data = placebo_panel)
rob_placebo <- tidy(did_mod_placebo, conf.int = TRUE) |> filter(term == "did_placebo")
```

Placebo DID estimate: **`r round(rob_placebo$estimate, 3)`**
(95% CI: [`r round(rob_placebo$conf.low, 3)`, `r round(rob_placebo$conf.high, 3)`],
p = `r round(rob_placebo$p.value, 4)`).
`r if_else(rob_placebo$p.value > 0.05, "Not significant — no pre-existing break detected. Parallel trends assumption supported.", "WARNING: significant — pre-existing trend break detected.")`

### Check 3: Alternative Outcome — All Offenses

Tests whether STAR diverted calls rather than suppressing all crime broadly.
The effect should be stronger for STAR-targeted offenses than for all
offenses combined.

```{r}
#| label: rob-all
#| include: false
panel_all <- crime_clean |>
  count(neighborhood_id, treated, post_star, did_term, year_month, name = "incidents") |>
  complete(neighborhood_id,
           year_month = seq(min(year_month), max(year_month), by = "month"),
           fill = list(incidents = 0)) |>
  mutate(treated   = as.integer(neighborhood_id %in% treated_nbhds),
         post_star = as.integer(year_month >= star_date),
         did_term  = treated * post_star)

did_mod_all <- lm(incidents ~ factor(neighborhood_id) + factor(year_month) + did_term,
                  data = panel_all)
rob_all <- tidy(did_mod_all, conf.int = TRUE) |> filter(term == "did_term")
```

All-offense DID estimate: **`r round(rob_all$estimate, 3)`**
(95% CI: [`r round(rob_all$conf.low, 3)`, `r round(rob_all$conf.high, 3)`],
p = `r round(rob_all$p.value, 4)`).

### Check 4: Alternative Control Group — High-Volume Neighborhoods Only

The treated neighborhoods are downtown and high-volume. This check restricts
the control group to neighborhoods whose pre-STAR average monthly incident
rate falls in the top quartile, making them more structurally comparable to
the treated neighborhoods.

```{r}
#| label: rob-comparable
#| include: false
pre_means <- analysis_panel |>
  filter(post_star == 0) |>
  group_by(neighborhood_id, treated) |>
  summarise(pre_mean = mean(incidents), .groups = "drop")

q75 <- quantile(pre_means$pre_mean[pre_means$treated == 0], 0.75)

comparable_controls <- pre_means |>
  filter(treated == 0, pre_mean >= q75) |>
  pull(neighborhood_id)

panel_comparable <- analysis_panel |>
  filter(treated == 1 | neighborhood_id %in% comparable_controls)

did_mod_comparable <- lm(incidents ~ factor(neighborhood_id) + factor(year_month) + did_term,
                         data = panel_comparable)
rob_comparable <- tidy(did_mod_comparable, conf.int = TRUE) |> filter(term == "did_term")
```

Control restricted to **`r length(comparable_controls)`** neighborhoods with
pre-STAR average ≥ `r round(q75, 1)` incidents/month.
DID estimate: **`r round(rob_comparable$estimate, 3)`**
(95% CI: [`r round(rob_comparable$conf.low, 3)`, `r round(rob_comparable$conf.high, 3)`],
p = `r round(rob_comparable$p.value, 4)`).

## Figure 5: Robustness Summary

```{r}
#| label: fig-5
#| fig-cap: "All DID estimates across specifications. Point = estimate; bar = 95% CI; blue = main specification. If the main estimate is robust, all non-placebo specifications should fall on the same side of zero."
#| fig-height: 3.5
results_summary <- bind_rows(
  mutate(did_result,     spec = "Main DID (STAR-targeted offenses)"),
  mutate(rob_all,        spec = "Alternative outcome: all offenses"),
  mutate(rob_comparable, spec = "Alternative control: high-volume nbhds"),
  mutate(rob_placebo,    spec = "Placebo (treatment = Jun 2019)")
) |>
  select(spec, estimate, conf.low, conf.high, p.value) |>
  mutate(across(c(estimate, conf.low, conf.high), \(x) round(x, 3)),
         p.value = round(p.value, 4))

results_summary |>
  mutate(spec = fct_rev(factor(spec))) |>
  ggplot(aes(x = spec, y = estimate, ymin = conf.low, ymax = conf.high,
             colour = spec == "Main DID (STAR-targeted offenses)")) +
  geom_pointrange(size = 0.8) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey40") +
  coord_flip() +
  scale_colour_manual(values = c("TRUE" = "#2166ac", "FALSE" = "#636363"),
                      guide = "none") +
  scale_y_continuous(labels = comma) +
  labs(x = NULL,
       y = "Differential monthly STAR-targeted incidents per neighborhood") +
  theme_minimal(base_size = 11)
```

\newpage

# Section 4: Managerial Implications

```{r}
#| label: managerial
#| include: false
est              <- did_result$estimate
n_pilot          <- 8
months_pilot     <- 15
n_all_nbhds      <- n_distinct(analysis_panel$neighborhood_id)

monthly_avoided  <- abs(est) * n_pilot
total_avoided    <- monthly_avoided * months_pilot
annualized       <- monthly_avoided * 12
citywide_monthly <- abs(est) * n_all_nbhds
```

The DID estimate of **`r round(est, 2)`** incidents per neighborhood per
month means STAR
`r if_else(est < 0, "reduced", "increased")`
STAR-targeted incidents in the pilot neighborhoods relative to the control
trend after launch.

**Quantified impact across the 8 pilot neighborhoods:**

- Monthly incidents avoided: **`r round(monthly_avoided, 1)`**
- Total avoided over the 15-month pilot (Jun 2020 – Aug 2021):
  **`r round(total_avoided, 0)`**
- Projected annualized reduction: **`r round(annualized, 0)`** incidents/year

**Implications for expansion:**

If the per-neighborhood effect holds city-wide, scaling STAR to all
`r n_all_nbhds` Denver neighborhoods could avoid approximately
**`r round(citywide_monthly, 0)`** STAR-targeted incidents per month across
the city. Each avoided incident represents a 911 call handled without police
dispatch, freeing officer capacity for higher-priority calls.

**Geographic targeting:** Because the pilot neighborhoods are
disproportionately high-volume, expansion should prioritize other
high-density districts first. Extending to low-volume residential
neighborhoods would likely yield a smaller absolute benefit per dollar spent.

**Caveats for decision-makers:**

1. Incident counts reflect *reported* events. STAR may also reduce
   unreported incidents not captured in this dataset.
2. The post-period overlaps substantially with COVID-19 (June 2020 onward),
   which independently suppressed crime city-wide. Month fixed effects absorb
   this common shock, but the 15-month post-period is short and results
   should be interpreted with appropriate caution.
3. A full cost-effectiveness analysis would require STAR's per-dispatch cost
   compared to average police-response cost — data not available in the
   crime incident dataset used here.
